Analysis of split plot design using MCMCglmm

### 2017-06-01 Analysis.Rmd
Update analysis for tiller incidence
Add description to the Analysis describing how data load and where scripts are

@@

# Separate the TRT column into the two treatments for analysis
AUDPS <- separate(data = AUDPS, col = TRT, into = c("WMGT", "NRTE"))

>>>>

The analyses are semi-automated. When this file is knit, it automatically loads the _ProjectTemplate_ package and calls the `load.project()` function. This loads the data, cleans and munges it creating the `AUDPS` data frame used for the analysis below. The scripts used to clean and munge the data are located in the [munge](./munge) folder and numbered in the sequential order in which they are run.

@@

# Separate the TRT column into the two treatments for analysis
AUDPS <- separate(data = AUDPS, col = TRT, sep = "_", into = c("WMGT", "NRTE"))
